\documentclass[12pt,oneside]{MastersDoctoralThesis_dry_en}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage{lscape}
\usepackage{rotating}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{bm}
\DeclareMathOperator{\var}{Var}
\AtBeginDocument{\setstretch{1.15}}
\setlength{\parindent}{1.3em}
\setlength{\parskip}{0pt}

\captionsetup[table]{
  font=small,
  labelfont=bf,
  justification=centering,
  singlelinecheck=false,
  margin=0pt
}

%----------------------------------------------------------------------------------------
%   UTILITIES
%----------------------------------------------------------------------------------------

\usepackage{verbatim}
\usepackage{epigraph}
\usepackage{enumitem}
\usepackage{tikz}
\usetikzlibrary{positioning,arrows.meta,shapes.geometric,calc,shapes.multipart}

\usepackage{pdflscape}
\usepackage{graphicx}
\usepackage{caption}

\usepackage{float}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{threeparttable}
\usepackage{array}
\usepackage{longtable}
\usepackage{tcolorbox}
\usepackage{caption}
\usepackage{xcolor}

% Placeholder macro for headline numbers awaiting the matched-protocol
% pipeline completion. Renders in red bold until replaced with final text.
% Grep the source for \PH{ to find every pending number.
\newcommand{\PH}[1]{\textcolor{red}{\textbf{#1}}}

\usepackage[
  backend=biber,
  style=authoryear,
  maxcitenames=2,
  mincitenames=1,
  maxbibnames=99
]{biblatex}

\newcommand{\tabcite}[1]{\citeauthor{#1} (\citeyear{#1})}

\addbibresource{example.bib}
\usepackage[autostyle=true]{csquotes}

%----------------------------------------------------------------------------------------
%   PAGE LAYOUT
%----------------------------------------------------------------------------------------

\geometry{
    paper=a4paper,
    inner=2.7cm,
    outer=2.4cm,
    bindingoffset=0.2cm,
    top=2.4cm,
    bottom=2.5cm,
    includefoot
}


\usepackage{ragged2e}

%----------------------------------------------------------------------------------------
%   DRY CHAPTER / SECTION STYLE
%----------------------------------------------------------------------------------------

\usepackage[explicit]{titlesec}

% No “Chapter 1” line in strong emphasis: only a small chapter number above the title.
\titleformat{\chapter}[display]
  {\normalfont\centering}
  {\normalfont\normalsize\thechapter}
  {0.35ex}
  {\Large\bfseries #1}

% Fix: \centering in \titleformat{\chapter} leaks into body text.
% Patch LaTeX's post-heading hook to restore justified alignment.
\makeatletter
\g@addto@macro\@afterheading{%
  \global\leftskip\z@
  \global\rightskip\z@
  \global\parfillskip\z@ plus 1fil\relax}
\makeatother

\titlespacing*{\chapter}{0pt}{0.9cm}{1.1cm}

\titleformat{\section}
  {\normalfont\large\bfseries}
  {\thesection}{0.8em}{#1}

\titleformat{\subsection}
  {\normalfont\normalsize\bfseries}
  {\thesubsection}{0.8em}{#1}

\titleformat{\subsubsection}
  {\normalfont\normalsize\itshape}
  {\thesubsubsection}{0.8em}{#1}

\titlespacing*{\section}{0pt}{2.2ex plus .6ex minus .2ex}{0.9ex}
\titlespacing*{\subsection}{0pt}{1.9ex plus .5ex minus .2ex}{0.6ex}
\titlespacing*{\subsubsection}{0pt}{1.5ex plus .4ex minus .2ex}{0.4ex}

\captionsetup{
  font=small,
  labelfont=bf,
  justification=justified,
  singlelinecheck=false,
  margin=0pt
}

\clearpairofpagestyles
\ohead*{\pagemark}
\pagestyle{plain}
\setchapterpagestyle{plain}

%----------------------------------------------------------------------------------------
%   THESIS INFORMATION
%----------------------------------------------------------------------------------------

\thesistitle{Do Health Policy Conclusions Survive Modern DiD? Re-estimating TWFE Studies}
\supervisor{Cristine \textsc{Pinto} \\ Pedro H. C. \textsc{Sant'Anna}}
\examiner{}
\degree{Master's}
\author{Victor \textsc{Rangel}}
\addresses{}

\subject{Public Policy}
\keywords{}
\university{{Insper}}
\department{{Master in Public Policy}}
\faculty{{Center for Management and Public Policy}}

\AtBeginDocument{
\hypersetup{pdftitle=\ttitle}
\hypersetup{pdfauthor=\authorname}
\hypersetup{pdfkeywords=\keywordnames}
}

\begin{document}

\frontmatter
\pagestyle{plain}

%----------------------------------------------------------------------------------------
%   TITLE PAGE
%----------------------------------------------------------------------------------------

\begin{titlepage}
\begin{center}

\vspace*{.06\textheight}
{\textcolor{Red}{\scshape\LARGE \bfseries \univname}\par}\vspace{.5cm}
{\textcolor{Red}{\scshape\large Professional Master's Program in Public Policy}\par}\vspace{1cm}

\textsc{\Large Master's Dissertation}\\[0.5cm]

\HRule \\[0.4cm]
{\huge \bfseries \ttitle\par}\vspace{0.4cm}
\HRule \\[1.5cm]
 
\begin{minipage}[t]{0.4\textwidth}
\begin{flushleft} \large
\emph{Author:}\\
{\textcolor{Red}{\authorname}}
\end{flushleft}
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}
\begin{flushright} \large
\emph{Advisors:} \\
{\textcolor{Red}{\supname}}
\end{flushright}
\end{minipage}\\[3cm]
 
\vfill

\large \textit{Dissertation submitted to the Professional Master's Program in Public Policy as partial fulfillment of the requirements for the degree of}\\[0.3cm]
{\textcolor{red}{\deptname}}\\[1cm]

\vfill
\end{center}
\end{titlepage}

%----------------------------------------------------------------------------------------
%   ABSTRACT
%----------------------------------------------------------------------------------------

\clearpage
\phantomsection
\addchaptertocentry{\abstractname}
\thispagestyle{plain}

\vspace*{0.8cm}

\begin{center}
{\small\scshape \univname\par}

\vspace{0.6cm}

{\Large\itshape Abstract\par}

\vspace{0.5cm}

{\bfseries \ttitle\par}

\vspace{0.3cm}

by \authorname
\end{center}

\vspace{0.8cm}

\noindent
Difference-in-differences (DiD) estimates in health-policy research often inform welfare, cost-effectiveness, and policy-ranking calculations. These uses depend on magnitude, not only on sign. This research re-estimates the headline results of 53 published health-economics DiD papers that used two-way fixed effects (TWFE), replacing TWFE with a standardized set of modern heterogeneity-robust estimators and diagnostics. The goal is empirical. It asks how often published conclusions survive modern re-estimation, and along which margins they change.

\medskip

\noindent
The results show broad sign stability but substantial interpretive instability. The sign of the effect is preserved in 46 cases and reverses in 7, an 86.8\% preservation rate. Sixteen articles lose conventional statistical significance under the modern benchmark. Point estimates move by more than 50\% in 39.6\% of designs and by more than 100\% in 24.5\%. Negative weights are present in many staggered TWFE designs, but they are not the dominant source of divergence in this sample. Larger differences arise from control-group choice, covariate handling, dynamic aggregation, endpoint binning, support at long horizons, and software defaults. HonestDiD exercises also show that robustness to treatment-effect heterogeneity does not imply robustness to violations of parallel trends.

\medskip

\noindent
The contribution is to document how the modern DiD critique changes interpretation in a defined published literature. The evidence does not show that the health-economics DiD literature collapses. It shows that many conclusions weaken along margins that matter for policy interpretation. The research produces two practical outputs: a pre-submission checklist and a design-triage decision tree for applied DiD work. The exercise is restricted to binary absorbing-treatment DiD designs in health economics.
%----------------------------------------------------------------------------------------
%   ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------

\begin{acknowledgements}
\addchaptertocentry{\acknowledgementname}

I am grateful to my advisors, Cristine Pinto and Pedro H.~C. Sant'Anna, for
their guidance, intellectual generosity, and patience throughout this project.
Pedro's open-source implementations of modern DiD methods made the empirical
exercise possible, and Cristine's feedback shaped every stage of the design and
writing. I thank Insper's Center for Management and Public Policy for the
institutional support that made the Master's possible, and the faculty of the
Professional Master's Program in Public Policy for the classes and conversations
that preceded this work.

This dissertation builds on the replication packages kindly released by the
original authors of the studies I reanalyze. Science advances because
researchers make their data and code available, and this project is in their
debt.

Finally, I thank my family and friends for their support during the writing of
this dissertation.

\end{acknowledgements}

%----------------------------------------------------------------------------------------
%   TABLE OF CONTENTS, LIST OF FIGURES, LIST OF TABLES
%----------------------------------------------------------------------------------------

\tableofcontents
\listoffigures
\listoftables

%----------------------------------------------------------------------------------------
%   THESIS CONTENT - CHAPTERS
%----------------------------------------------------------------------------------------

\mainmatter
\pagestyle{plain}

\include{Chapters/Chapter1}
\include{Chapters/Chapter2}
\include{Chapters/Chapter3}
\include{Chapters/Chapter4}
\include{Chapters/Chapter5}

%----------------------------------------------------------------------------------------
%   BIBLIOGRAPHY
%----------------------------------------------------------------------------------------

\printbibliography[heading=bibintoc,title={References}]

%----------------------------------------------------------------------------------------
%   APPENDICES
%----------------------------------------------------------------------------------------

\appendix

%\include{Appendices/AppendixA}
%\include{Appendices/AppendixB}
%\include{Appendices/AppendixC}
%\include{Appendices/AppendixD}
%\include{Appendices/AppendixE}

\end{document}
