\chapter{Introduction}
\label{Chapter1}

Two-way fixed-effects (TWFE) has been the default estimator for difference-in-differences (DiD) in applied health economics for decades. Over the past five years, the methodological literature has shown that TWFE can produce estimates that look like causal parameters but combine cohort-time contrasts in ways the researcher did not intend \parencite{goodman2021difference,sun2021estimating,callaway2021difference,roth2023s}. The question this paper asks is narrow and empirical: \textit{when we replace TWFE with a modern heterogeneity-robust estimator in published health-economics DiD studies, how often --- and on what margin --- do the conclusions change?}

We re-estimate the headline result of 53 published health-economics DiD studies under a standardized modern-estimator protocol. The sign of the effect is preserved in 47 of the 53 cases and reverses in 6. Statistical significance is lost in 14 of the originally significant estimates, and the standard error rises by a median of 36\%. The within-paper proportional shift in the point estimate ranges from $-431\%$ in \textcite{maclean2025paid} to $+542\%$ in \textcite{levine2011effective}. Modern DiD estimators rarely overturn published health-policy conclusions. They routinely weaken them.

This headline conceals substantial within-paper heterogeneity. 32\% of estimates shift by more than 50\% in magnitude, and 21\% shift by more than 100\% (see Figure~\ref{fig:ch3_aggregate_variation}, Section~\ref{Chapter4}). The width of that distribution is the empirical substance of the exercise. When a policy's cost-benefit ratio depends on the size of the treatment effect --- the typical case in health --- a 50\% or 100\% magnitude shift can flip the adoption decision even when the sign does not move. The relevant empirical margin is magnitude, not sign alone.

The contribution of this paper is to identify \textit{which} design margins account for the TWFE-vs-modern gap in this literature. Three findings reframe the applied debate.

First, the negative-weights critique that has organized methodological attention since \textcite{goodman2021difference} is empirically second-order. In our staggered subsample, the mean share of negative weights is \textbf{6.4\%} and the median is \textbf{0.4\%} (Table~\ref{tab:bacon_summary}). These are smaller numbers than the popular mental model would suggest. The dominant sources of divergence lie elsewhere: control-group choice (Lesson~6), covariate handling (Lesson~7, where 33 of 36 originally-controlled papers compare TWFE-with-covariates to unconditional CS-DID), dynamic aggregation (Lesson~9, where 12 of 52 papers change classification across aggregation rules), endpoint binning (Lesson~4, with a median $|\Delta| = 34\%$ under progressive binning across 21 papers), and software defaults (Lesson~10).

Second, robustness to treatment-effect heterogeneity does not imply robustness to parallel-trends violations. The median HonestDiD breakdown value \parencite{rambachan2023more} at the first post-treatment period is zero under both TWFE and CS-DID (Lesson~5). Switching to a heterogeneity-robust estimator sharpens the mapping from the coefficient to an estimand but does not rescue designs whose identifying counterfactual is itself fragile. These are two separate questions, and the applied literature still tends to conflate them.

Third, the ten empirical lessons in Section~\ref{Chapter4} condense into a one-page pre-submission checklist (Box~4.1 in Section~\ref{sec:applied_guide}) whose items are calibrated to the empirical prevalence of each failure mode in this sample. This checklist is the paper's intended practical deliverable and is complementary, not alternative, to the conceptual framework of \textcite{baker2025difference}.

Compared to prior reanalysis exercises in finance and accounting \parencite{baker2022much}, political science \parencite{chiu2023and}, and cross-field reproducibility \parencite{brodeur2026reproducibility}, this paper goes deeper rather than wider. Those studies establish the \emph{prevalence} of TWFE-vs-modern divergence across many fields; we \emph{decompose} the divergence within one field, isolating the contribution of five design margins --- binning, geographic conditioning, control-group choice, covariate handling, and software defaults --- that the prior literature treats as secondary to the negative-weights critique. To our knowledge, this is the first applied reanalysis to systematically document the joint contribution of these margins in any published DiD literature, and the only one to report that the negative-weights share itself is empirically second-order (mean $0.064$, Table~\ref{tab:bacon_summary}) once the larger design margins are surfaced. Health economics is a natural site for this decomposition: DiD is the workhorse identification design in the subfield \parencite{goldsmith2024tracking} and the policy stakes are unusually explicit, because welfare and cost-effectiveness calculations depend directly on the magnitude of the estimated treatment effect.

The rest of the paper is organized as follows. Section~\ref{Chapter2} reviews the methodological and reanalysis literatures that motivate the exercise. Section~\ref{Chapter3} describes the 53-article sample, the standardized re-estimation protocol, the identification assumptions that discipline the external validity of our meta-statistic (Section~\ref{sec:identification}), and the AI-assisted workflow. Section~\ref{Chapter4} presents ten lessons organized around the empirical mechanisms behind TWFE-vs-modern divergence (§§4.1--4.10), culminating in the pre-submission checklist (§\ref{sec:applied_guide}). Section~\ref{Chapter5} concludes. Per-article results, HonestDiD sensitivity analyses, and Bacon decompositions are documented in Appendix~\ref{AppendixB}; the AI-assisted pipeline in Appendix~\ref{AppendixC}; the sample-construction log in Appendix~\ref{AppendixD}.
