\chapter{Empirical Design}
\label{Chapter3}

\section*{Notation}
\label{sec:notation}

Table~\ref{tab:notation} lists the symbols, acronyms, and technical terms used throughout the paper. Each row gives a one-line definition and a pointer to the section where the object is first used or defined; default values apply unless an article's metadata overrides them.

\begin{table}[!htbp]
\centering
\small
\caption{Notation and technical terms}
\label{tab:notation}
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}p{3.5cm} p{9cm} p{2cm}@{}}
\toprule
\textbf{Symbol / term} & \textbf{Definition} & \textbf{First use} \\
\midrule
\multicolumn{3}{l}{\textit{Estimators}} \\
TWFE                              & Two-way fixed-effects regression with unit and time fixed effects                                      & \S\ref{Chapter2} \\
CS-DID                            & \textcite{callaway2021difference} difference-in-differences                                             & \S\ref{Chapter2} \\
CS-NT                             & CS-DID with never-treated comparison group                                                              & \S\ref{Chapter3} \\
CS-NYT                            & CS-DID with not-yet-treated comparison group                                                            & \S\ref{Chapter3} \\
SA                                & \textcite{sun2021estimating} event-study estimator                                                      & \S\ref{Chapter2} \\
BJS (Gardner)                     & \textcite{borusyak2024revisiting} imputation estimator; here the \texttt{did2s} implementation of \textcite{gardner2022two} & \S\ref{Chapter3} \\
dCdH                              & \textcite{dechaisemartin2020twfe} TWFE decomposition / \texttt{did\_multiplegt\_dyn} estimator          & \S\ref{Chapter2} \\
HonestDiD                         & \textcite{rambachan2023more} sensitivity framework for parallel-trends violations                       & \S\ref{Chapter2} \\
\addlinespace
\multicolumn{3}{l}{\textit{Causal parameters and aggregations}} \\
$ATT(g,t)$                        & Average treatment effect on cohort $g$ at time $t$ (Callaway--Sant'Anna's building block)               & \S\ref{Chapter2} \\
$CATT$                            & Cohort-specific ATT; same object as $ATT(g,t)$ when indexed by cohort alone                             & \S\ref{Chapter2} \\
Group aggregation                 & \texttt{aggte(type="group")} --- average within each cohort, then across cohorts                         & \S\ref{Chapter3} \\
Simple aggregation                & \texttt{aggte(type="simple")} --- direct average across all $(g,t)$ cells                                & \S\ref{Chapter3} \\
Dynamic aggregation               & \texttt{aggte(type="dynamic")} --- average across cohorts at each event-time horizon                     & \S\ref{Chapter3} \\
\addlinespace
\multicolumn{3}{l}{\textit{Event-study horizons and binning}} \\
$e$                               & Event time: periods relative to first treatment ($e=0$ is the adoption period)                         & \S\ref{Chapter3} \\
$F_K$, $L_K$                      & Far-pre and far-post endpoint bins ($e \leq -K_{\text{pre}}$ and $e \geq K_{\text{post}}$)             & \S\ref{sec:binning} \\
$\hat\beta_{k=0}$, $\hat\beta_{k_{\max}}$ & Far-post coefficient when the bin holds only the terminal horizon ($k=0$) versus absorbing all distant horizons ($k_{\max}$) & \S\ref{sec:binning} \\
$\Delta$                          & Progressive-binning sensitivity: $(\hat\beta_{k_{\max}} - \hat\beta_{k=0}) / |\hat\beta_{k=0}|$        & Table~\ref{tab:progbin_sensitivity} \\
\addlinespace
\multicolumn{3}{l}{\textit{Panel structure and balancing}} \\
Balanced (R)                      & Keep only units observed in every period; \texttt{did::att\_gt(allow\_unbalanced\_panel=FALSE)} internal pair-balancing when data happen to be balanced & \S\ref{sec:li_sensitivity} \\
Unbalanced (R)                    & Use all available observations; \texttt{did::att\_gt(allow\_unbalanced\_panel=TRUE)}                    & \S\ref{sec:li_sensitivity} \\
Pair-balanced (Stata)             & Stata's \texttt{csdid2}: for each $(g,t)$, retain units observed in base period and in $t$             & \S\ref{sec:li_sensitivity} \\
Fill rate                         & Fraction of $(\text{unit} \times \text{time})$ cells observed in the panel                              & \S\ref{Chapter3} \\
Base period (universal / varying) & Reference period for event-study normalization: $g-1$ (universal, CS--standardised) or $t-1$ (varying, Stata default) & \S\ref{sec:li_sensitivity} \\
\addlinespace
\multicolumn{3}{l}{\textit{Goodman-Bacon decomposition}} \\
$\omega_j$                        & Weight on the $j$-th $2\times 2$ DiD in the Bacon decomposition of the TWFE estimand                    & \S\ref{Chapter2} \\
TvU, EvL, LvE                     & Treated-vs-Untreated, Earlier-vs-Later-treated, Later-vs-Earlier-treated $2\times 2$ components         & Table~\ref{tab:bacon_summary} \\
TvT share                         & Combined share of EvL and LvE weights --- the treated-versus-treated comparisons                        & Table~\ref{tab:bacon_summary} \\
\addlinespace
\multicolumn{3}{l}{\textit{HonestDiD}} \\
$\bar M$                          & Breakdown value under Rambachan--Roth relative-magnitude restrictions (the smallest $\bar M \geq 0$ at which the confidence interval covers zero) & Table~\ref{tab:ch3_honestdid} \\
$\bar M_{\text{first}}$           & $\bar M$ evaluated at the first post-treatment period                                                    & Table~\ref{tab:ch3_honestdid} \\
$\bar M_{\text{peak}}$            & $\bar M$ evaluated at the post-treatment event-time coefficient with the largest $|t|$                  & Table~\ref{tab:ch3_honestdid} \\
\addlinespace
\multicolumn{3}{l}{\textit{Sample and protocol}} \\
$N_1$, $N_0$                      & Size of the reanalyzed sample and of the excluded population. The pipeline processed $N_1=56$ articles; three were excluded on structural grounds (Myers~2017, Moorthy-Shaloka~2025, Kuziemko et al.~2018), leaving $N_1=53$ in the comparable subsample used for fidelity-sensitive aggregates. $N_0=1{,}828$ in both cases.                 & \S\ref{sec:selection_bounds} \\
$\pi$, $\hat\pi_1$, $\pi_0$       & Population, in-sample, and excluded-subsample sign-preservation rates                                    & \S\ref{sec:selection_bounds} \\
\texttt{xformla}                  & \texttt{did::att\_gt} argument for the conditional-parallel-trends covariate set                        & \S\ref{Chapter3} \\
\texttt{cs\_controls\_matched}    & Metadata flag triggering matched-protocol CS-DID with \texttt{xformla = $\sim$twfe\_controls} (Deliverable D1) & \S\ref{Chapter4} \\
\texttt{cs\_sample\_filter}       & Metadata field letting CS-DID skip the global \texttt{sample\_filter}; empty string means CS runs on the full pre-filter data (e.g.\ paper 241, where TWFE is estimated on the paper's event-window subsample but CS-DID needs the full balanced panel). & Appendix~\ref{AppendixC} \\
\texttt{cs\_min\_e} / \texttt{cs\_max\_e} & Metadata fields clipping the CS-DID dynamic aggregation to a paper-specified event-time window. & Appendix~\ref{AppendixC} \\
\bottomrule
\end{tabular*}
\end{table}

\section{Sample, protocol, and scope}

The reanalysis draws on \textit{health economics} articles published between 2000 and 2025 in 17 general-interest and field journals. From 8,171 candidate articles retrieved from OpenAlex, an LLM-based screen of abstracts flags 1,884 as likely \emph{DiD} studies. We then search for replication materials, consolidate records across sources, deduplicate by DOI, and manually review 431 located cases for eligibility. The final sample contains 56 articles that use \emph{DiD} as the main empirical strategy and provide a full replication package, allowing the main specification to be re-estimated under a common protocol. Table~\ref{tab:sample_pipeline} summarizes the selection process and Appendix~\ref{AppendixD} documents each stage of the collection pipeline in detail.

Of the 56 reanalyzed articles, 32 use staggered adoption and 24 one-time adoption. Thirty-eight use panel data and 18 use \emph{repeated cross-sections} (RCS), and 50 have an estimable dynamic \emph{event study}. Table~\ref{tab:sample_detailed} cross-tabulates adoption type and data structure. These dimensions determine estimator coverage and the construction of the counterfactual. The sample covers topics such as vaccination, insurance regulation, opioids, pollution, maternal and child health, tax credits, and epidemics. Table~\ref{tab:journal_final} reports the journal distribution, and Appendix~\ref{AppendixB} lists the reanalyzed studies.


\begin{table}[!htbp]
\centering
\caption{Sample construction pipeline}
\label{tab:sample_pipeline}
\begin{threeparttable}
\small
\begin{tabular}{p{.6cm} p{4cm} p{4.2cm} p{1.2cm} p{2.5cm}}
\toprule
\textbf{Step} & \textbf{Procedure} & \textbf{Retention criterion} & \textbf{$N$} & \textbf{Note} \\
\midrule
1 & Candidate articles in the search universe & Selected journals, 2000--2025 & 8,171 & 17 journals \\
\midrule
2 & Identification of \emph{DiD} strategy & Article uses \emph{DiD} as the main empirical strategy & 1,884 & Automated AI-based classification \\
\midrule
3 & Location and manual screening of materials & Article with replication material located and eligible for individual review & 431 & Individual review of the 431 candidates \\
\midrule
4 & Completed reanalysis & Main specification re-estimable under the standardized protocol & 56 & Final sample \\
\bottomrule
\end{tabular}
\begin{tablenotes}[flushleft]
\footnotesize
\item Notes: $N$ is the number of articles retained at the end of each stage. Step~1 is the total number of candidate articles downloaded via OpenAlex from the selected journals, including all articles from the health journals and articles with health-related keywords in the remaining journals. Step~2 applies an AI-assisted classifier that assesses whether the \emph{abstract} describes a \emph{DiD} strategy. Step~3 consolidates the five search sources described in the text and deduplicates by DOI. Step~4 involves human supervision: assessment of package quality, identification of the main specification, and exclusion if necessary.
\end{tablenotes}
\end{threeparttable}
\end{table}



\input{Tables/table_3_2_sample_detailed.tex}

\input{Tables/table_3_3_journal_final.tex}

The unit of analysis is the article's main specification. For each study, we preserve the central empirical result and re-estimate it with alternative econometric tools. Doing so requires a consistent rule to select one outcome and one main specification per article, while avoiding case-by-case discretion. Selection follows a simple hierarchy. We first prioritize specifications explicitly described by the authors as main, preferred, or baseline. If more than one candidate remains, we choose the one estimated on the largest number of observations. In the event of a tie, we apply three tie-breakers, in this order: preference for the most aggregated outcome variable (e.g., all-cause mortality over cause-specific categories), then for specifications with fewer time-varying covariates, and, only as a last resort, a documented random selection. When the article reports only a dynamic event study, with no directly comparable static ATT, we re-estimate a collapsed version with a single post-treatment indicator while preserving the sample, controls, fixed effects, and clustering level of the original study. All decisions are recorded in an auditable log described in Appendix~\ref{AppendixA}.

\section{Identification and scope of the meta-statistic}
\label{sec:identification}

\noindent\textbf{Identification.} The central meta-statistic of the paper --- the share of the 56 reanalyzed articles whose original TWFE conclusion is preserved under the standardized modern-estimator protocol --- targets the rate at which a representative published health-economics DiD study would survive modern re-estimation. This interpretation rests on two maintained assumptions.

\textit{Representativeness of the 56-paper sample.} The 56 reanalyzed articles are assumed to be representative of the larger population of 1,884 DiD candidate articles identified at Step~2 of the sample construction pipeline (Table~\ref{tab:sample_pipeline}) along the design margins that drive TWFE-vs-modern divergence: control-group choice, covariate set, dynamic aggregation rule, endpoint binning, geographic conditioning, and software defaults. This assumption is partially testable. Table~\ref{tab:selection_balance} reports observable-characteristic balance between the reanalyzed sample and a 537-article DiD-classified pool retained during sample construction, on publication year and journal tier. The reanalyzed sample trends slightly more recent (mean 2019.9 vs 2018.4, Welch $p=0.010$) and is heavily over-represented in AEJ-family journals (50.9\% vs 2.5\%) and in \emph{Review of Economics and Statistics} (18.9\% vs 1.0\%), while under-represented in field journals (24.5\% vs 95.2\%; all $p<0.001$). This concentration reflects the data-and-code policies of these venues and confirms that the reanalyzed sample is not a random draw from the DiD literature: it is the ``replication-package-available subset,'' skewed toward publication venues with strict reproducibility requirements. Because the 97\% attrition from 1,884 to 56 is concentrated at Step~3 (location and screening of replication materials), the selection effect plausibly biases the headline numbers toward the more careful end of the published literature. Where this margin matters for interpretation, we flag it explicitly in the text and, in Section~\ref{Chapter5}, discuss how robust the qualitative conclusions are to that bias.

\input{Tables/table_3_selection_balance.tex}

\textit{Estimator recovery by the reanalysis protocol.} Conditional on each article's declared specification and the design margins above, the AI-assisted reestimation protocol is assumed to recover the modern estimator that the original authors would have selected had they worked from the modern-DiD toolkit available in 2026. This assumption is not formally testable within this study. The protocol is deterministic for a fixed random seed, and the eleven held-out calibration articles (Appendix~\ref{AppendixC}) match the hand-coded benchmark exactly. That validation speaks to execution fidelity but not to the counterfactual estimator choice the original authors themselves would have debated had they rewritten the paper in 2026.

If either assumption fails in a direction correlated with the survival outcome, the headline meta-statistic should be read as an internal descriptive fact about the 56-article sample rather than as a population parameter. Throughout the paper, we frame our findings as diagnoses of the 56 studies we actually re-estimated and are explicit when we extrapolate more broadly.

\subsection{Selection bounds on the population preservation rate}
\label{sec:selection_bounds}

Because representativeness is an untested assumption, we complement the point estimate with worst-case bounds in the style of \textcite{manski1989anatomy}. Of the 56 reanalyzed articles, 48 preserve the sign of the original TWFE conclusion under the modern-estimator protocol, a within-sample preservation rate of $\hat\pi_1 = 48/56 = 85.7\%$. Let $\pi_0$ denote the (unobserved) preservation rate among the $N_0 = 1{,}828$ articles excluded during sample construction. The population-level preservation rate is a weighted average,
\[
\pi = \frac{N_1 \hat\pi_1 + N_0 \pi_0}{N_1 + N_0} = \frac{47 + 1{,}831\,\pi_0}{1{,}884},
\]
where $N_1 = 53$ is the comparable subsample (the 56 reanalyzed articles minus the three structural exclusions). Without further assumptions, $\pi_0 \in [0, 1]$ implies the uninformative Manski bound $\pi \in [2.5\%, 99.8\%]$.

Tightening the bound requires an assumption about the excluded population. Table~\ref{tab:selection_bounds} reports implied population rates under five scenarios for $\pi_0$. Under Manski--Pepper monotone selection --- the assumption that excluded articles have weakly lower replication-package quality and hence weakly lower preservation under modern re-estimation, so that $\pi_0 \leq \hat\pi_1$ --- the population rate satisfies $\pi \leq 88.7\%$. This is the directionally informative bound we take forward: the within-sample rate we report is an \emph{upper bound} on the population parameter, not an unbiased estimate.

\begin{table}[!htbp]
\centering
\caption{Selection-bound scenarios for the population preservation rate}
\label{tab:selection_bounds}
\small
\begin{tabular}{lccr}
\toprule
\textbf{Scenario for excluded rate $\pi_0$} & $\pi_0$ & \textbf{Implied population rate $\pi$} & \textbf{vs $\hat\pi_1$} \\
\midrule
Worst case (all excluded would fail)     & $0\%$  & $2.5\%$   & $-86.2$ pp \\
Lower quartile                            & $25\%$ & $27.0\%$  & $-61.7$ pp \\
Half of excluded preserve                 & $50\%$ & $51.6\%$  & $-37.1$ pp \\
Upper quartile                            & $75\%$ & $76.1\%$  & $-12.6$ pp \\
Representativeness ($\pi_0 = \hat\pi_1$)  & $88.7\%$ & $88.7\%$ & $0$ pp  \\
Best case (all excluded preserve)         & $100\%$& $99.8\%$  & $+11.1$ pp \\
\bottomrule
\end{tabular}
\begin{flushleft}\footnotesize
\textit{Notes:} $\hat\pi_1 = 47/53 = 88.7\%$ is the within-comparable-subsample sign-preservation rate under the \texttt{chapter\_statistics.R} classification (same-sign between TWFE and CS-DID dynamic aggregate; 47 preserved and 6 reversed, matching the counts reported in Section~\ref{Chapter4}). $N_0 = 1{,}831$ is the count of articles outside the reanalyzed sample (1{,}884 candidate DiD articles minus the 53 comparable subsample). Under Manski--Pepper monotone selection ($\pi_0 \leq \hat\pi_1$), the population rate is bounded above by $\hat\pi_1$; the worst-case lower bound is $47/1{,}884 = 2.5\%$. Comparison column $\Delta\mathrm{pp} = \pi - \hat\pi_1$ in percentage points.
\end{flushleft}
\end{table}

Two caveats accompany Table~\ref{tab:selection_bounds}. First, the scenarios are illustrative: we do not claim that the true $\pi_0$ equals any particular number in the range. Second, the 97\% attrition from 1,884 to 56 is concentrated at Step~3 --- location of replication materials --- and the selection mechanism is likely correlated with paper quality, author seniority, and journal data-sharing policies. A full balance analysis comparing observable characteristics of the 56 included articles against a random sample of the 1,828 excluded articles would sharpen the scenario selection; we report this exercise in future work and acknowledge here that the chosen scenarios, while informative about sensitivity, do not resolve the underlying selection question.

\section{Estimators and coverage}

We re-estimate each article's main specification with different econometric tools. We reproduce the \emph{two-way fixed effects} (\emph{TWFE}) model as the baseline estimator, keeping the basic structure of the original article whenever possible. We do not audit the authors' code line by line. The goal is to reconstruct the original result in a standardized environment and compare it to modern estimators.

Our primary alternative is the estimator of \textcite{callaway2021difference} with dynamic agreggation. We use it because it accommodates treatment-effect heterogeneity under staggered adoption, makes the comparison group explicit, and allows versions with covariates and dynamic paths comparable to the \emph{event studies} used in the literature. Whenever the design allows, we estimate two CS-DID versions, one with a \emph{never-treated} comparison group and another with a \emph{not-yet-treated} group. We also estimate, when applicable, Sun and Abraham and Gardner (\texttt{did2s}).\footnote{The choice of \texttt{did2s} as an additional estimator mainly reflects operational convenience and broad compatibility with the designs observed in the sample, including \emph{repeated cross-sections}.} These estimators serve as cross-checks rather than replacements for the main benchmark. They indicate whether the main results survive different ways of handling heterogeneity, aggregation, and counterfactual construction.

Not all estimators are used in every part of the reanalysis, and not all articles have an estimable pre-treatment path. In this paper, the static benchmark is based on TWFE, CS-NT, and CS-NYT, with CS-DID serving as the main modern DiD reference. Gardner and Sun \& Abraham are used in the dynamic analysis as robustness checks for event-study profiles, following a methodological choice of this paper rather than a limitation of those estimators. Appendix~\ref{AppendixB} presents the individual results, event studies, and sensitivity analyses for each of the 56 articles. Table~\ref{tab:estimator_coverage} summarizes estimator coverage under this protocol.

\input{Tables/table_3_4_estimator_coverage.tex}


\section{AI-assisted estimation and calibration protocol}

Reanalyzing 56 articles required a workflow that could handle heterogeneous replication packages without changing the estimation layer across studies. We built a semi-automated protocol adapted from the separation between substantive judgment and standardized execution emphasized by \textcite{xu2026scaling} and the broader use-case catalog for generative AI in economic research surveyed by \textcite{korinek2023generative}. The workflow has three stages, illustrated in Figure~\ref{fig:ai_workflow}. A profiling stage reads the article PDF and replication code to extract a structured specification file. An estimation stage feeds this specification into a fixed template that runs all applicable estimators, producing point estimates and event-study outputs. A reporting stage assembles the results into a standardized comparison with the original finding. The estimation template is the same for every article, and differences across studies enter only through the specification file and through documented preprocessing choices. Appendix~\ref{AppendixC} documents the full architecture, the metadata contract, and all pipeline stages in detail\footnote{The structured specification files, estimation scripts, outputs, and protocol-revision logs are available in the replication package.}.

We developed the protocol through a supervised calibration exercise based on 11 articles previously analyzed by hand. For each of these articles, the semi-automated workflow was asked to reconstruct the design from scratch under the standardized execution rules, without relying on the original hand-coded implementation. The resulting estimates were then compared against the manual benchmark. Any discrepancy triggered a diagnostic review, followed by revisions to the protocol until the automated reconstruction matched the benchmark sufficiently closely. This process produced a catalog of 28 recurring implementation problems and their corresponding resolution rules.\footnote{Examples include Stata date encodings, missing standard errors in plotting routines, silent dropping of horizons in event-study implementations, singular matrices in small-cohort CS-DID estimation, contamination of the never-treated comparison group by late-treated units, and differences between cumulative and marginal event-study aggregation across software. The full catalog is documented in Appendix~\ref{AppendixC}.} Once the workflow reliably reproduced the calibration set, it was extended to the remaining 45 articles in the sample. The researcher reviewed each specification before execution, inspected each event-study output, and approved all decisions involving sample restrictions, treatment timing, controls, and cross-estimator comparability. When an article required preprocessing beyond the default rules, that adjustment was encoded through standardized specification fields and documented for replication.\footnote{These cases included, for example, composite treatment indicators, time-varying treatment within units, and individual-level repeated cross-sections requiring aggregation.}


\begin{figure}[!htbp]
\centering

\begin{tikzpicture}[
  node distance=1.6cm,
  every node/.style={font=\small},
  box/.style={
    draw,
    rectangle,
    minimum width=6.2cm,
    minimum height=1.1cm,
    text width=5.8cm,
    align=center
  },
  doublebox/.style={
    box,
    double,
    double distance=1.5pt
  },
  arrow/.style={
    thick,
    -{Stealth[length=2.5mm]}
  },
  label/.style={
    font=\footnotesize,
    inner sep=1pt
  }
]

% --- Main flow ---
\node[box] (manual)
  {Manual analysis of 11 calibration articles};

\node[box, below=of manual] (profiler)
  {LLM extracts structured specifications\\from PDF and replication code};

\node[box, below=of profiler] (analyst)
  {Fixed estimation template runs estimators\\(TWFE, CS, SA, Gardner)};

\node[box, below=of analyst] (compare)
  {Compare with manual benchmark};

\node[box, below=2.4cm of compare] (expand)
  {Apply calibrated pipeline\\to 45 new articles};

\node[doublebox, below=of expand] (review)
  {Human review of specifications,\\event studies, and results};

% --- Side box ---
\node[doublebox, right=2.5cm of compare, minimum width=4.2cm, text width=3.8cm]
  (knowledge) {Diagnose failure,\\update protocol log};

% --- Main vertical arrows ---
\draw[arrow] (manual)  -- (profiler);
\draw[arrow] (profiler) -- (analyst);
\draw[arrow] (analyst) -- (compare);
\draw[arrow] (expand)  -- (review);

% --- Match arrow (compare → expand) with label ---
\draw[arrow] (compare) -- (expand)
  node[label, midway, left] {match};

% --- Mismatch arrow (compare → knowledge) ---
\draw[arrow] (compare) -- (knowledge)
  node[label, midway, above] {mismatch};

% --- Loop arrow (knowledge → profiler) ---
\draw[arrow] (knowledge.north) |- ([xshift=3pt]profiler.east)
  node[label, pos=0.25, right, text width=2cm, align=left]
  {revise \\protocol\\(28 patterns)};

\end{tikzpicture}

\caption{Calibration and expansion workflow for AI-assisted reanalysis}
\label{fig:ai_workflow}
\end{figure}

The three-stage workflow above (Profiler, Analyst, Reporter) is the computational backbone that produces each article's estimates. To verify that those estimates are \emph{implemented correctly given each paper's own specification} and that they \emph{match the number printed in the original paper}, the pipeline is augmented with a per-paper audit layer documented in Appendix~\ref{AppendixC}. That audit layer reviews the implementation of every estimator against its package documentation (CS-DID, HonestDiD, Bacon, and the dCdH family), compares the stored coefficient to the paper's reported value, and records the outcome in per-article reports that accompany the replication package. Aggregate fidelity statistics from this audit enter the comparable-subsample size reported above (53 of 56 articles).
