\chapter{Conclusion}
\label{Chapter5}


Health-policy decisions often turn on the magnitude of a DiD estimate. Sign preservation does not settle the decision when the relevant threshold lies between two competing estimates. This dissertation asked how stable those magnitudes are under modern DiD estimators. It reassessed 53 health-economics studies under a common replication and re-estimation protocol. The literature does not collapse. Most results remain directionally recognizable, but many become less secure once the identifying comparison is made explicit. Instability in this sample appears less often as sign reversal and more often as shifts in magnitude, weaker dynamic profiles, loss of precision, and greater sensitivity to design choices than the original articles suggested.

The contribution is empirical and comparative. Re-estimating a defined applied literature under a common protocol separates results that remain stable from results that weaken once the design is interrogated along the margins modern DiD estimators force into view. That distinction reframes how the recent critique of TWFE should be read in practice. Disagreement in this sample is not driven mainly by negative weights. It more often reflects control-group choice, the role of covariates, aggregation, support at long horizons, endpoint binning, and implementation. The practical implication is that TWFE should not remain the default primary estimator in applied DiD. Modern estimators address heterogeneous-treatment-effect bias and also make the causal contrast transparent, exposing design choices that TWFE compresses inside a single coefficient.

The applied output is condensed into two artefacts at the end of Section~\ref{sec:applied_guide}. Box~4.1 is a fifteen-item pre-submission checklist anchored to the empirical patterns documented in the reanalysis. Figure~\ref{fig:decision_tree} is a design-triage guide for choosing the primary modern specification and for deciding which sensitivity margins belong in the main text. Together they translate the reanalysis into a workflow that helps researchers state the estimand, defend the untreated comparison, treat the event study as a design diagnostic, and make implementation choices visible before the result is presented as causal evidence. They complement design reasoning rather than replace it.

The exercise has clear limits. The sample is restricted to studies with usable replication materials and does not represent the full DiD literature. The analysis depends on the data and code environments provided by the original authors and inherits limitations from those replication packages. Coverage is concentrated in health economics and skewed toward studies set in the United States, which constrains generalization across fields and institutional settings. Several replications required adaptations to make the original specifications compatible with a standardized implementation in R. Modern estimators have their own limits. In designs with weak overlap, small samples, or high-dimensional covariates, they clarify the estimand at the cost of precision. The dissertation's claim is correspondingly narrow. It delivers an auditable and comparable reassessment of a defined literature, not a census of DiD applications.

These limits point to natural extensions. The core problem identified in this dissertation is not specific to TWFE in the canonical staggered binary case. It is the broader question of whether the empirical implementation keeps the causal target, the identifying comparison, and the available support aligned. Richer treatment settings make that alignment harder to see. Three extensions follow directly.

The first is triple-difference designs. Applying a comparable protocol to health settings with eligibility or geographic partitions, such as Medicaid expansions interacted with income bands or programs that vary across states and cohorts, would carry the decomposition by design margin into a richer identifying structure.

The second is non-absorbing treatments. \textcite{dechaisemartin2020twfe} handle policy on-and-off dynamics that the current sample excludes by construction. Those estimators are the natural instrument for revisiting health-policy studies with reversible treatment, such as temporary Medicaid expansions or short-duration mandates.

The third is designs with compositional change. \textcite{sant2026difference} accommodate shifts in the composition of treated units over time, a setting common to health-policy studies where eligibility rules evolve during the study window.

The reanalysis of a literature is a pointed intervention. What this exercise leaves behind is a more demanding discipline of design justification, auditable, comparable, and portable to any DiD literature willing to reexecute the question.