\section{AI-Assisted Reanalysis Pipeline}
\label{AppendixC}

This appendix documents the automated pipeline used to reanalyze 53 TWFE studies with modern DiD estimators. The architecture follows the framework proposed by \textcite{xu2026scaling}, who show that large-scale reanalysis can be organized as a multi-layer system where a language-model orchestrator coordinates deterministic computational agents through structured file-based communication. \textcite{xu2026scaling} evaluate their framework on 92 instrumental-variable studies, of which 67 have manually verified reproducible 2SLS estimates and 25 are newly published, analyzing up to three specifications per paper (215 total) across seven pipeline stages, and report 87\% end-to-end success. The present project adapts their core principles to a three-stage DiD-specific workflow covering 53 articles.

\subsection{Calibration and Scaling Strategy}
\label{sec:calibration}

The pipeline was developed through a process analogous to supervised learning. The ``training set'' consisted of 11 articles that had already been reanalyzed manually in earlier work by the author, for which the correct TWFE and CS-DID estimates were known. The ``test set'' comprised the remaining 42 articles, which the pipeline would process semi-automatically once calibration was complete.

Calibration proceeded as an iterative loop. In each iteration, the LLM orchestrator (Claude Sonnet 4, Anthropic 2025, accessed through Claude Code) was instructed to reanalyze all 11 calibration articles from scratch, with no memory of previous attempts. The orchestrator read each article's PDF and replication code, filled \texttt{metadata.json}, and invoked the fixed R template. The resulting TWFE and CS-DID estimates were then compared against the known manual results. Two validation thresholds governed acceptance. The reestimated TWFE coefficient had to match the original paper's estimate exactly (up to rounding), and the CS-DID estimate had to fall within 10\% of the manually obtained value (allowing for minor R-vs-Stata implementation differences in \texttt{att\_gt}). When an article failed either threshold, the failure was diagnosed, and a new entry was added to the knowledge base (\texttt{failure\_patterns.md}) recording the context, root cause, and resolution rule. The loop was then restarted. The orchestrator reprocessed all 11 articles, now reading the updated knowledge base before each profiling step, so that previously encountered pitfalls were avoided without relearning. Over successive iterations, the knowledge base grew from zero to 28 documented patterns by the end of the calibration phase, and the pass rate on the calibration set converged to 100\%. The catalog has continued to grow during the expansion phase and post-calibration revision; at the time of this writing it stands at over 50 patterns, all of them version-controlled.

This design mirrors the logic of supervised learning. Labeled examples (manual estimates) provide the loss signal, the knowledge base acts as the learned parameters, and successive iterations reduce error until the system generalizes to unseen articles. The difference from statistical learning is that each ``parameter update'' is an interpretable, version-controlled text entry, making the accumulated knowledge auditable and transferable.

Once all 11 calibration articles passed both thresholds, the pipeline entered its second phase, processing the remaining 42 articles semi-automatically. For each new article, the LLM orchestrator read the PDF and replication code, filled \texttt{metadata.json}, and invoked the R template, consulting the full 28-pattern knowledge base throughout. Human review was required at two checkpoints, approving the Profiler's specification choices (Stage~1) and diagnosing any Analyst failures (Stage~2). New failures encountered on expansion articles were added to the knowledge base. This two-phase design ensures that the pipeline is validated against known ground truth before processing unseen articles, and that the knowledge base provides institutional memory preventing the system from repeating resolved failures.

\subsection{Design Principles}

The pipeline rests on a strict separation between scientific reasoning and computational execution. The LLM reads papers and makes specification decisions, while a fixed R script handles all estimation. The two layers communicate exclusively through a structured JSON file (\texttt{metadata.json}), so that no analytical choice is hidden inside code modifications. The R template is never modified per article, and all article-specific logic resides in \texttt{metadata.json}. Given identical metadata and data, the template produces identical results, eliminating a class of replication failures tied to ad-hoc script edits. Implementation failures are recorded in a version-controlled knowledge base (\texttt{failure\_patterns.md}) that the orchestrator reads before profiling each new article, allowing the system to avoid previously encountered pitfalls without relearning them. All inter-stage communication is file-based, so an interrupted run can be resumed from the last completed stage without loss.

\subsection{Architecture}

The system is organized in three layers (Figure~\ref{fig:pipeline_arch}). Layer~1 is the LLM orchestrator, governed by a master instruction file (\texttt{CLAUDE.md}) that defines the project scope, directory structure, estimator selection rules, and safety constraints. Layer~2 comprises three skill files (\texttt{SKILL\_profiler.md}, \texttt{SKILL\_analyst.md}, \texttt{SKILL\_reporter.md}) that define the contract for each pipeline stage, together with a knowledge base (\texttt{failure\_patterns.md}) that accumulates implementation lessons across articles. Layer~3 is the execution layer, a single fixed R script (\texttt{did\_analysis\_template.R}) that performs all estimation deterministically.

\begin{figure}[H]
\centering
\begin{tcolorbox}[colback=gray!5, colframe=gray!60, width=\textwidth, title=Pipeline Architecture]
\footnotesize
\begin{verbatim}
Layer 1: LLM Orchestrator (CLAUDE.md)
  |
  |--- reads ---> Layer 2: Skill files + Knowledge base
  |                 |--- SKILL_profiler.md
  |                 |--- SKILL_analyst.md
  |                 |--- SKILL_reporter.md
  |                 |--- failure_patterns.md (28 patterns)
  |
  |--- coordinates ---> 3-Stage Pipeline:
  |
  |  [Stage 1: PROFILER]      [Stage 2: ANALYST]       [Stage 3: REPORTER]
  |  PDF + Code + Data --->   metadata.json + Data --> results.csv + PDF
  |       |                        |                        |
  |  metadata.json            results.csv              report.md
  |                           event_study.pdf
  |
  '--- executes ---> Layer 3: did_analysis_template.R (fixed)
\end{verbatim}
\end{tcolorbox}
\caption{Three-layer architecture for AI-assisted DiD reanalysis. The LLM orchestrator (Layer~1) reads skill descriptions and failure patterns (Layer~2) to fill article-specific metadata, which drives a fixed R template (Layer~3).}
\label{fig:pipeline_arch}
\end{figure}


\subsection{Pipeline Stages}

\noindent\textbf{Stage 1: Profiler.}\enspace
The Profiler reads the article PDF (\texttt{pdf/[id].pdf}) and the replication package (\texttt{data/[id]/}) to produce \texttt{results/[id]/metadata.json}. It examines the methodology section and main results table to identify the outcome variable, treatment indicator, unit of observation, time period, and whether treatment adoption is staggered or single-date. It then reads the replication code (\texttt{.do} or \texttt{.R} files) to extract exact variable names, sample restrictions, control variables, and clustering choices, and inspects the data file to confirm that variable names match (case-sensitive in R).

When multiple specifications are reported, the Profiler applies a hierarchical selection protocol. It first looks for a specification explicitly labeled ``main,'' ``preferred,'' or ``baseline.'' If no such label exists, it selects the specification with the most observations. If still tied, it chooses the one with fewest time-varying controls, and if still tied, it uses the first specification presented. The Profiler then fills all fields of \texttt{metadata.json} (see Section~\ref{sec:metadata_contract}) and validates internal consistency. In particular, \texttt{run\_csdid\_nyt} and \texttt{run\_bacon} are set to \texttt{true} if and only if treatment timing is staggered, and \texttt{has\_event\_study} reflects the original paper.

\medskip
\noindent\textbf{Stage 2: Analyst.}\enspace
The Analyst takes \texttt{results/[id]/metadata.json} and the raw data as input, producing \texttt{results/[id]/results.csv} and, when applicable, \\\texttt{results/[id]/event\_study.pdf}. The entire estimation runs through a single command, \texttt{Rscript templates/did\_analysis\_template.R [id]}. The template reads \\\texttt{metadata.json} and performs estimations conditional on flags set by the Profiler. TWFE is always estimated via \texttt{fixest::feols} with unit and time fixed effects and clustered standard errors. CS-DID with never-treated controls is always estimated via \texttt{did::att\_gt} with \texttt{control\_group = "nevertreated"}, aggregated to a scalar ATT via \texttt{aggte}. When treatment adoption is staggered, the template additionally runs CS-DID with not-yet-treated controls and a Bacon decomposition (\texttt{bacondecomp::bacon}). If the original paper reports an event study, Sun-Abraham estimates are obtained via \texttt{fixest::feols} with \texttt{sunab()}, and Gardner estimates via \texttt{did2s::did2s}.

\medskip
\noindent\textbf{Stage 3: Reporter.}\enspace
The Reporter reads \texttt{results.csv}, \texttt{event\_study.pdf}, and \\\texttt{metadata.json} to produce a structured report (\texttt{results/[id]/report.md}) covering six sections, from article summary through specification, point estimates, comparison with the original finding, event study assessment, and conclusion. The conclusion classifies each reanalysis as \textit{confirmed} (CS-DID and TWFE agree in sign and significance, with magnitude difference below 20\%), \textit{partial} (same sign and significance but magnitude differs by 20\% or more, or marginal significance change), or \textit{challenged} (sign reversal, or one estimator significant while the other is not).


\subsection{The Metadata Contract}
\label{sec:metadata_contract}

The \texttt{metadata.json} file is the sole interface between the Profiler (scientific reasoning) and the Analyst (deterministic computation). Table~\ref{tab:metadata_fields} documents its key fields.
\begin{longtable}{>{\ttfamily\footnotesize\raggedright}p{6.0cm} >{\small\raggedright\arraybackslash}p{9.0cm}}
\caption{Key fields of \texttt{metadata.json}.} \label{tab:metadata_fields} \\
\toprule
\textnormal{\textbf{Field}} & \textbf{Description} \\
\midrule
\endfirsthead
\toprule
\textnormal{\textbf{Field}} & \textbf{Description} \\
\midrule
\endhead
\midrule
\multicolumn{2}{r}{\footnotesize\itshape Continued on next page} \\
\endfoot
\bottomrule
\endlastfoot

id & Mapping ID for the article \\
title & Full article title \\
group\_label & Category: \texttt{escalonada\_controles}, \texttt{escalonada\_sem\_controles}, \texttt{unica\_controles}, or \texttt{unica\_sem\_controles} \\
data.file & Path to the data file relative to project root \\
data.sample\_filter & R expression applied via \texttt{dplyr::filter()} \\[3pt]
variables.outcome & Outcome variable name \\
variables.unit\_id & Panel unit identifier \\
variables.time & Time period variable \\
variables.treatment\_twfe & Binary post-treatment indicator for TWFE \\
variables.gvar\_cs & Cohort variable for CS-DID (0 = never-treated) \\
variables.twfe\_controls & Time-varying controls in the TWFE regression \\
variables.cs\_controls & Controls passed to \texttt{att\_gt(xformla=)} \\
variables.cluster & Clustering variable for standard errors \\
variables.weight & Observation weights \\
variables.additional\_fes & Extra fixed effects beyond unit + time \\[3pt]
panel\_setup.data\_structure & \texttt{"panel"} or \texttt{"repeated\_cross\_section"} \\
panel\_setup.treatment\_timing & \texttt{"staggered"} or \texttt{"single"} \\[3pt]
analysis.run\_csdid\_nyt & Run CS-DID with not-yet-treated controls \\
analysis.run\_bacon & Run Bacon decomposition \\
analysis.has\_event\_study & Whether the original paper reports an event study \\
analysis.event\_pre & Number of pre-treatment periods in the event window \\
analysis.event\_post & Number of post-treatment periods in the event window \\[3pt]
preprocessing.time\_recode & Mapping for non-contiguous time periods \\
preprocessing.construct\_vars & R expressions evaluated before estimation \\[3pt]
original\_result.beta\_twfe & Original TWFE coefficient (for validation) \\

\end{longtable}

The \texttt{preprocessing.construct\_vars} field deserves particular attention. Because the R template is never modified, any article-specific data manipulation (constructing a treatment indicator, creating a cohort variable, recoding missing values) must be expressed as R code strings in this array. These expressions are evaluated sequentially within the template's data environment before any estimation begins. A typical entry might define a post-treatment indicator as \texttt{"df\$Post\_avg <- as.integer(df\$year >= df\$treat\_year \& df\$treated == 1)"} or filter missing observations as \texttt{"df <- df \%>\% filter(!is.na(df\$outcome\_var))"}. This mechanism keeps the template fixed while accommodating the heterogeneity of 53 different replication packages.


\subsection{Knowledge Base}

Large-scale reanalysis is inherently iterative, as \textcite{xu2026scaling} emphasize, because the system encounters novel implementation failures that must be diagnosed, resolved, and remembered. This project addresses that challenge through a version-controlled knowledge base (\texttt{knowledge/failure\_patterns.md}). Each entry records the estimation step and data configuration that triggered the failure, the underlying technical reason, and a reusable corrective instruction.

Over the course of analyzing 53 articles, 28 patterns were documented across five categories. Estimator output extraction patterns (1--4, 19) deal with Sun-Abraham's \texttt{iplot} returning no SE column (1), Gardner/did2s term naming differing from Stata (2), negative horizons being silently dropped (3), and individual-level repeated cross-sections being incompatible with BJS (4, 19). CS-DID estimation patterns (5, 8, 15, 22--26, 42--43) cover singular covariance matrices in small cohorts (5), repeated cross-section panel configuration (8), cohort variables that vary within units (15), BJS aggregation requirements (22), time-varying treatment incompatibility (23), base-period selection and cumulative-versus-marginal effect discrepancies between R and Stata (24, 26), late-treated units incorrectly absorbed into the never-treated group (25), propensity score overfitting with geographic dummies (42), and integer truncation of infinity in cohort variables (43). Stata-to-R data translation patterns (7, 9--12, 16) handle half-year and monthly date formats (7, 12), non-contiguous time periods (9), filter syntax differences (10), treatment variable construction (11), and Stata's \texttt{xi}-expanded variable names (16). Event study construction patterns (13--14, 18, 20--21) resolve tail-bin renaming that inflates the post-treatment average (13), incorrect cohort identification from pre-treatment dummies (14), never-treated unit exclusion (18), control-variable collinearity with event dummies (20), and article-specific sample restrictions in event studies (21). A TWFE specification pattern (17) addresses articles that use plain OLS without fixed effects, where the template's mandatory unit and time FEs produce a systematic ${\sim}10\%$ divergence from the original estimate. One additional pattern (6) documents a Windows-specific file-locking issue with PDF output.

The orchestrator reads this knowledge base before profiling each new article. When a known pattern is recognized, such as Stata monthly dates, the Profiler preemptively applies the resolution rule in \texttt{metadata.json} rather than discovering the failure at the Analyst stage.


\subsection{Directory Structure}

The complete project directory is organized as follows.

\begin{tcolorbox}[colback=gray!5, colframe=gray!60, width=\textwidth]
\footnotesize
\begin{verbatim}
replication_analysis/
  CLAUDE.md                        # Master instructions (Layer 1)
  skills/
    SKILL_profiler.md              # Profiler contract (Layer 2)
    SKILL_analyst.md               # Analyst contract (Layer 2)
    SKILL_reporter.md              # Reporter contract (Layer 2)
  knowledge/
    failure_patterns.md            # Failure patterns (Layer 2)
  templates/
    did_analysis_template.R        # Fixed R template (Layer 3)
  data/
    [id]/                          # Replication data per article
  pdf/
    [id].pdf                       # Article PDFs
  results/
    [id]/
      metadata.json                # Profiler output
      results.csv                  # Analyst output
      event_study.pdf              # Event study (if applicable)
      report.md                    # Reporter output
  start_information/               # Reference materials (read-only)
\end{verbatim}
\end{tcolorbox}


\subsection{Replication Instructions}

Replicating or extending this project requires R (version $\geq$ 4.4) with the following packages installed: \texttt{fixest}, \texttt{did}, \texttt{did2s}, \texttt{bacondecomp}, \texttt{haven}, \texttt{dplyr}, \texttt{ggplot2}, \texttt{tidyr}, \texttt{jsonlite}. It also requires access to an LLM capable of reading PDFs and structured files (this project used Claude Sonnet 4, Anthropic 2025, accessed through Claude Code, with the instruction set in \texttt{CLAUDE.md}).

To add a new article, place the article PDF in \texttt{pdf/[id].pdf} and the replication package in \texttt{data/[id]/}, and create an empty directory \texttt{results/[id]/}. The Profiler stage, following \texttt{SKILL\_profiler.md}, reads the article and replication code to fill \texttt{results/[id]/metadata.json}. This step requires scientific judgment in identifying the main specification, mapping variable names, and determining whether adoption is staggered. The knowledge base (\texttt{failure\_patterns.md}) should be consulted for known pitfalls. The Analyst stage then runs \texttt{Rscript templates/did\_analysis\_template.R [id]}. If the script fails, the error should be diagnosed, \texttt{metadata.json} corrected, and the script rerun. New failure patterns should be added to the knowledge base with the standard three-field structure. The Reporter stage, following \texttt{SKILL\_reporter.md}, reads \texttt{results.csv} and \texttt{event\_study.pdf} to write \texttt{results/[id]/report.md} with the standardized classification (confirmed, partial, or challenged).

For articles in the calibration set described in Section~\ref{sec:calibration}, validation involves comparing the template output against the manual estimates. TWFE should match the original paper exactly (up to rounding). CS-DID may differ slightly due to R vs.\ Stata implementation differences (acceptable threshold $\leq 10\%$). New articles without prior manual analysis should be spot-checked by inspecting the \texttt{metadata.json} specification choices and verifying that the reestimated TWFE reproduces the original paper's coefficient.


\subsection{From three-stage pipeline to nine-agent architecture}
\label{sec:nine_agent_architecture}

The three-stage pipeline documented above is the computational core. Running it delivers a coefficient; verifying that the coefficient is trustworthy requires two additional layers. Across the iterative development of this project the architecture therefore grew into a nine-agent system, documented here. The original three stages (Profiler, Analyst, Reporter) remain unchanged; the six additional agents operate on top of their outputs.

\noindent\textbf{Methodology audit layer (five reviewers).}
Each reviewer owns one estimator family and is strictly read-only. The \texttt{twfe-reviewer} validates the FE structure, clustering, weights, and covariates of the TWFE regression against the paper's own specification, with particular attention to the Pattern 50 sample-mismatch invariant (identical sample must enter TWFE and CS-DID unless an explicit \texttt{cs\_sample\_filter} or \texttt{cs\_construct\_vars} is declared). The \texttt{csdid-reviewer} audits \texttt{did::att\_gt} usage: control group choice, \texttt{xformla}, base period, and balancing flags. The \texttt{bacon-reviewer} determines whether \texttt{bacondecomp::bacon} is formally applicable (balanced panel + staggered adoption) and interprets the treated-vs-treated (TvT) weight share as an attenuation-risk signal. The \texttt{honestdid-reviewer} checks the event-study inputs fed into \texttt{HonestDiD}, computes the $\bar M$ breakdown values under Rambachan--Roth relative-magnitude restrictions, and translates them into the D-ROBUST / D-MODERATE / D-FRAGILE scale. The \texttt{dechaisemartin-reviewer} advises when the \texttt{DIDmultiplegtDYN} estimator would add information --- essentially when treatment is reversible, continuous, or when TWFE and CS-DID disagree strongly and treatment reversal is suspected. Each reviewer emits PASS / WARN / FAIL plus a structured report.

\noindent\textbf{Fidelity audit layer (paper-auditor).}
The \texttt{paper-auditor} agent answers a separate, narrower question: does our stored coefficient match the number printed in the original paper? It is deliberately isolated from methodology --- if the paper's specification is itself problematic, that is the reviewers' concern, not the fidelity agent's. The paper-auditor opens \texttt{pdf/[id].pdf}, locates the paper's main/preferred/baseline specification using a four-level hierarchy (main $>$ preferred $>$ baseline $>$ column 1 of the headline table), extracts the coefficient, standard error, $N$, cluster level, and significance stars, and emits one of five verdicts: EXACT (relative gap $< 1\%$), WITHIN\_TOLERANCE ($< 5\%$), WARN ($5$--$20\%$), FAIL ($> 20\%$ or sign flip), or NOT\_APPLICABLE (the paper does not report a comparable scalar). Verdicts are written to \texttt{paper\_audit.md} per article and aggregated in \texttt{paper\_fidelity.csv}.

\medskip

On 2026-04-19 an audit-infrastructure bug was discovered: the \texttt{paper-auditor} had been invoked with the \texttt{Replication Package/} directory as working root but searched for \texttt{pdf/[id].pdf} directly under that root, while the PDFs lived at \texttt{../pdf/replicados/[id].pdf}. The result was that every reanalyzed article had returned NOT\_APPLICABLE on fidelity with the note ``no PDF found.'' After copying the relevant PDFs into the deposit at \texttt{pdf/[id].pdf} and re-running \texttt{paper-auditor} in parallel, the real fidelity distribution emerged: 36 EXACT, 5 WITHIN\_TOLERANCE, 8 NOT\_APPLICABLE, and 4 WARN across the 53-article sample. The three Step-4 drops documented in Appendix~\ref{AppendixD} (restricted-access mortality data; multivariate-with-trends TWFE baseline; county-specific linear trends combined with interacted FEs) are not part of the fidelity distribution because they are not part of the final sample.

\noindent\textbf{Orchestration and rating (skeptic).}
The \texttt{skeptic} agent composes the audit layer into a single per-paper credibility report. It invokes the five methodology reviewers and the paper-auditor in parallel for one article and synthesises their verdicts into one overall rating on a three-axis rubric. Axis~1 \emph{Fidelity} summarises the paper-auditor verdict: F-HIGH for EXACT/WITHIN\_TOLERANCE, F-MOD for WARN, F-LOW for FAIL, F-NA for NOT\_APPLICABLE. Axis~2 \emph{Implementation} aggregates the five reviewers: I-HIGH if all PASS, I-MOD if exactly one WARN, I-LOW if two or more WARN or any FAIL. The overall rating is a fixed table product: HIGH = F-HIGH $\times$ I-HIGH (or F-NA $\times$ I-HIGH when no PDF); MODERATE = one axis degraded; LOW = multiple degradations or implementation FAIL; VERY LOW used for catastrophic failures. Axis~3 \emph{Design credibility} reports D-ROBUST / D-MODERATE / D-FRAGILE / D-BROKEN as a \emph{separate finding} about the paper's identification strategy --- HonestDiD $\bar M$ breakdown values, Bacon TvT share, pre-trend patterns --- rather than as a demerit against the reanalysis. This separation was adopted mid-project after an initial run rated Kresch (2020) LOW for a faithfully-reproduced paper whose only ``problem'' was parallel-trends fragility; under the three-axis rubric the same paper rates HIGH with design fragility reported separately. That is the correct classification: the reanalysis is sound; the paper has an identification concern.

\noindent\textbf{Knowledge base (pattern-curator).}
The \texttt{pattern-curator} agent appends version-controlled entries to \texttt{knowledge/failure\_patterns.md} following a standard schema (Context / Root Cause / Resolution Rule / Examples). The catalog has grown from 28 patterns at the end of calibration to 51 after the iterative review phase. Notable additions since calibration include Pattern 42 (propensity-score overfitting in doubly-robust CS-DID with many time-varying controls), Pattern 49 (silent CS-DID sample mismatch with the TWFE sample --- the Kresch 2020 class bug), Pattern 50 (the sample-mismatch invariant now checked in \texttt{twfe-reviewer}), and Pattern 51 (RCS control collinearity silently inflating CS-DID ATT to false positive, discovered via the Levine-McKnight-Heep 2011 audit in April 2026).

\noindent\textbf{Repository stewardship (repo-custodian).}
The \texttt{repo-custodian} agent is the single git/GitHub steward. It owns \texttt{code/audit/full\_sync.sh} (which refreshes the \texttt{overleaf/} and \texttt{health\_did\_replication/} LaTeX projects from the canonical \texttt{Replication Package/}), the 24-check audit in \texttt{code/audit/run\_audit.R}, all commits and pushes, and verification that no raw data, secrets, or oversize files are staged. All other reviewer agents are read-only; only \texttt{repo-custodian} and \texttt{pattern-curator} may modify files under the canonical package.

\subsection{Iterative review pipeline}
\label{sec:iterative_review}

The audit layer described above is composed into an iterative per-paper review loop, applied during April 2026 to all papers not initially rated HIGH. For each paper the \texttt{skeptic} agent runs the six-reviewer audit and emits a draft rating, together with a list of candidate actions: metadata edits (re-specifying the FE structure, toggling \texttt{allow\_unbalanced}, adding or removing a \texttt{cs\_sample\_filter}, declaring a composite outcome, or retargeting the paper-auditor reference column), full-pipeline re-runs, or documentation notes in \texttt{metadata.notes}. The user chooses one action per paper; the \texttt{repo-custodian} applies the edit and re-runs the pipeline as needed; and the outcome is logged in \texttt{analysis/iterative\_review\_log.md} with before/after numerical comparison. Five CS-DID estimates that had previously returned NA or numerical collapse were recovered through metadata-only fixes: paper 241 (Soliman 2025) via a \texttt{cs\_sample\_filter = ""} opting CS-DID out of the paper's rel-year sample filter plus a \texttt{cs\_min\_e = -3, cs\_max\_e = 3} clip on the dynamic aggregation; papers 290, 309, and 311 via a toggle of \texttt{allow\_unbalanced} from \texttt{false} to \texttt{true}, resolving a \texttt{did\_standarization} balancing failure on unbalanced panels; and paper 201 via removal of a state-by-year pre-aggregation step that had been discarding all individual-level covariates before CS-DID. Paper 2303 (Cao \& Ma 2023) required a full 2.5-hour re-run at 14.8~GB memory peak to populate Spec B (TWFE without controls) and Spec A (CS-DID with the seven weather controls, doubly-robust) cells that had previously been NA and FAIL\_memory.

\subsection{Updated framework comparison}
\label{sec:updated_framework_comparison}

The table comparing this project to \textcite{xu2026scaling} elsewhere in this appendix is updated here to reflect the nine-agent architecture.

\begin{table}[H]
\centering
\caption{Framework comparison (updated): three-stage pipeline versus nine-agent architecture versus \textcite{xu2026scaling}.}
\label{tab:framework_comparison_updated}
\small
\begin{tabular}{>{\raggedright\arraybackslash}p{3.2cm}
                >{\raggedright\arraybackslash}p{3.8cm}
                >{\raggedright\arraybackslash}p{3.6cm}
                >{\raggedright\arraybackslash}p{3.6cm}}
\toprule
\textbf{Dimension} & \textbf{\textcite{xu2026scaling}} & \textbf{Initial 3-stage pipeline} & \textbf{Final 9-agent architecture} \\
\midrule
Scope                          & 92 IV studies (215 specs)                               & 53 DiD studies                                    & 53 DiD studies \\
Stages / agents                & 7 (Profiler, Librarian, Janitor, Runner, Skeptic, Journalist, QC) & 3 (Profiler, Analyst, Reporter)                   & 9 (original 3 + 5 methodology reviewers + paper-auditor + skeptic orchestrator + pattern-curator + repo-custodian) \\
Fidelity verification          & Final QC stage                                           & Manual spot-checks against metadata target         & \texttt{paper-auditor} agent running directly on PDF; 5-level verdict rubric \\
Methodology audit              & Not separate                                             & Ad-hoc                                             & Five dedicated read-only reviewers (TWFE, CS-DID, Bacon, HonestDiD, dChH) \\
Credibility rating             & Not explicit                                             & Not explicit                                       & Three-axis (Fidelity $\times$ Implementation $\to$ rating; Design credibility separate finding) \\
Knowledge base                 & Not explicitly described                                 & \texttt{failure\_patterns.md} (28 patterns)        & \texttt{failure\_patterns.md} (51 patterns) \\
Iterative review               & Not described                                            & Not described                                      & Per-paper loop with user decision log (\texttt{iterative\_review\_log.md}, 47 papers) \\
Primary challenge              & Volume (92 articles)                                     & Heterogeneity                                      & Heterogeneity $+$ fidelity verification $+$ design-vs-implementation disentangling \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Comparison with \textcite{xu2026scaling}}

Table~\ref{tab:framework_comparison} summarizes the main differences between the two frameworks. The primary distinction is scale versus depth. \textcite{xu2026scaling} process 92 articles with relatively homogeneous estimation (2SLS), whereas this project processes fewer articles but must handle substantial heterogeneity in data formats, variable encoding, and panel structure. The fixed-template design with \texttt{construct\_vars} preprocessing is this project's response to that heterogeneity. All idiosyncratic manipulation is expressed declaratively in \texttt{metadata.json}, keeping estimation code uniform across articles.

Both frameworks separate scientific reasoning (what to estimate) from computational execution (how to estimate it), treating this division as the central architectural decision for scalable reanalysis.

\begin{table}[H]
\centering
\caption{Framework comparison between \textcite{xu2026scaling} and the present project.}
\label{tab:framework_comparison}
\small
\begin{tabular}{>{\raggedright\arraybackslash}p{3.2cm}
                >{\raggedright\arraybackslash}p{5.5cm}
                >{\raggedright\arraybackslash}p{5.5cm}}
\toprule
\textbf{Dimension} & \textbf{\textcite{xu2026scaling}} & \textbf{Present project} \\
\midrule
Scope & 92 IV studies (215 specifications) & 53 DiD studies \\[4pt]
Estimators & 2SLS + first-stage F-stat & TWFE, CS-DID (NT/NYT), Sun-Abraham, Gardner, Bacon \\[4pt]
Pipeline stages & 7 (Profiler, Librarian, Janitor, Runner, Skeptic, Journalist, QC) & 3 (Profiler, Analyst, Reporter) \\[4pt]
Interface contract & Structured extraction fields & \texttt{metadata.json} (30+ fields) \\[4pt]
Execution layer & Custom Stata/R scripts & Single fixed R template \\[4pt]
Knowledge base & Not explicitly described & \texttt{failure\_patterns.md} (51 patterns, as of April 2026) \\[4pt]
Human-in-the-loop & Final QC stage & Profiler decisions and failure diagnosis \\[4pt]
Calibration & 67 manually verified studies & 11 articles with prior manual reanalysis \\[4pt]
Primary challenge & Volume (92 articles) & Heterogeneity (53 articles, each with unique data structure) \\
\bottomrule
\end{tabular}
\end{table}
