\section{Specification Selection Protocol and Decision Log}
\label{AppendixA}

This appendix documents the protocol used to select the main specification for each article and the log of decisions adopted.

\subsection{Selection Rule}

For each article, we select \emph{one} outcome and \emph{one} specification. The hierarchical rule is:

\begin{enumerate}[label=\roman*.]
  \item \textbf{Author declaration.} Specifications described as \emph{main}, \emph{preferred}, or \emph{baseline}.
  \item \textbf{Largest sample.} If more than one candidate remains, the specification with the largest $N$.
  \item \textbf{Tiebreakers:}
    \begin{enumerate}[label=(\alph*)]
      \item most aggregated variable;
      \item most parsimonious specification in time-varying covariates;
      \item documented random selection.
    \end{enumerate}
\end{enumerate}

When the article reports only a dynamic event study without a static ATT, we re-estimate a collapsed version with a single post-treatment indicator (Collapse = 1).

\newpage
\subsection{Decision Log}

\begin{small}
\setlength{\LTleft}{-1cm}
\setlength{\LTright}{-1cm}
\begin{longtable}{p{2.2cm} p{3.0cm} p{5.0cm} p{0.8cm} p{4.5cm}}
\caption{Main outcome selection by reanalyzed article}\label{tab:decision_log}\\
\toprule
\textbf{Article} & \textbf{Selected outcome} & \textbf{Rule applied \& rationale} & \textbf{Coll.} & \textbf{Textual quote} \\
\midrule
\endfirsthead
\toprule
\textbf{Article} & \textbf{Selected outcome} & \textbf{Rule applied \& rationale} & \textbf{Coll.} & \textbf{Textual quote} \\
\midrule
\endhead
\midrule
\multicolumn{5}{r}{\footnotesize\itshape continued on next page} \\
\endfoot
\bottomrule
\endlastfoot

% ===== CALIBRATION SET =====

\textcite{dranove2021dose}
& Log price per prescription (Table 4, col.~4)
& Rule i+iii --- declared preference. Footnote 23 defines col.~4 as preferred. Under iii(a), price is the primary focus of the article.
& 0
& ``column 4 our preferred estimate'' (fn.~23) \\

\textcite{buchmueller2018effect}
& GT4pres --- prescriptions from $>$4 physicians (Table 6, Panel B)
& Rule i --- declared preference. Doctor \emph{shopping} outcome is the article's main contribution.
& 0
& ``our preferred model combines these two categories of states into a single control group'' (p.~96) \\

\textcite{carrillo2019provider}
& Physicians per capita (Table 2, col.~5)
& Rule i --- declared preference. Physician supply is the main outcome; child health (Table 6) is supplementary.
& 0
& ``The estimated coefficient from our preferred specification that adjusts for all baseline controls'' (p.~175) \\

\textcite{bosch2014tradeoffs}
& Log employers $\leq$50 (Table 2, col.~7)
& Rule i+iii(a) --- ``Table 2 presents the main results''. Col.~7 aggregates firm sizes 1--50. Only event study reported.
& 1
& ``Table 2 presents the main results of the paper'' \\

\textcite{clemens2015regulatory}
& Private insurance coverage (Table 5, PA, col.~1)
& Rule i --- declared preference.
& 0
& ``I estimate equation~(4) as a check on the robustness of \ldots\ equation~(3) rather than as the baseline specification'' (p.~120) \\

\textcite{schmitt2018multimarket}
& Log non-medication price (Table 2, PA, col.~2)
& Rule i+ii --- ``Main results'' declared. Largest $N$ among main outcomes.
& 0
& ``additional models that modify various assumptions of the main analysis'' (p.~377) \\

\textcite{evans2014giving}
& Excellent/very good self-reported health (Table 3)
& Rule i+ii --- ``Main results'' declared. Largest $N$. Plain OLS without fixed effects (template adds FEs; $\sim$9\% divergence expected).
& 0
& ``unlike our main results, this specification cannot control for contemporaneous events impacting women with children'' (fn.~6) \\

\textcite{akosaantwi2013effects}
& Any health insurance (Table 2, col.~1)
& Rule i+iii(a) --- ``Main DD Results''. Any health insurance = most aggregated coverage measure.
& 0
& ``we are conservative in our use of equation~(1) as our main specification'' (p.~15) \\

\textcite{tanaka2014abolishing}
& Weight-for-age Z-score (Table 3, col.~5)
& Rule i --- declared preference.
& 0
& ``The preferred estimate in column~5 suggests that \ldots\ removing user fees improved WAZ'' (p.~292) \\

\textcite{lawler2023effect}
& Ever breastfed (Table 2, col.~1)
& Rule i+ii --- ``core finding'' declared. Largest $N$ (354,642).
& 0
& ``In the main tables we report standard difference-in-differences estimates \ldots'' \\

\textcite{carpenter2019direct}
& Prob.\ receiving 1 dose Tdap, ages 10--12 (Table 1, col.~1)
& Rule i+iii(b) --- ``main results'' declared. Between the two outcomes in Table 1, col.~1 has the largest $N$ (116,304) and is more parsimonious.
& 0
& ``Our main results are not sensitive to removing the controls in the Z vector.'' (p.~107) \\

\textcite{marcus2022long}
& Sports club membership (Table 2, col.~3)
& Rule i --- declared preference.
& 0
& ``In our third and preferred specification, we augment equation~(2) with municipality fixed effects'' (p.~138) \\

\textcite{bhalotra2021urban}
& Under-5 mortality rate, diarrheal/respiratory diseases (Table 3, col.~1)
& Rule ii+iii(c) --- Table with respiratory controls has largest $N$. Documented random tiebreaker between panels.
& 0
& ``We view the specifications using respiratory diseases as controls as the most conservative.'' (p.~504) \\

\textcite{levine2011effective}
& Private insurance (Table 5, PA, col.~2)
& Rule i+ii --- SCHIP (Table 3) is main, but uses age discontinuity (not amenable to the template). Secondary parental coverage analysis (Table 5, staggered DiD) is amenable.
& 0
& ``Table 3 shows our main results for SCHIP'' \\

\textcite{hoynes2015income}
& \% low birthweight (Table 2, col.~1)
& Rule i+ii+iii(b) --- ``Main Estimates''. Largest $N$. Most parsimonious.
& 0
& ``Our main estimates are for a `high-impact sample'\,\ldots\, Results from estimating equation (1) \ldots\ are shown in Table 2.'' \\

\textcite{greenstone2014environmental}
& PM --- mean particulate matter (Equation 2C)
& Rule i+iii(a) --- ``Preferred econometric specification''. PM = most aggregated pollutant. Two-stage procedure (template approximation).
& 1
& ``In the preferred econometric specification that controls for city fixed effects, year fixed effects, and differential preexisting trends among adopting cities'' (p.~3041) \\

% ===== EXPANSION SET =====

\textcite{maclean2025paid}
& Childcare hours, minutes/day (Appendix Table 10)
& Rule i --- Main estimator is Gardner (did2s); TWFE reported in Appendix Table~10.
& 0
& ``we use the Gardner (2022) approach in our main specification'' (p.~7) \\

\textcite{li2025shortened}
& Log drug price (Table 3, col.~3)
& Rule i --- TWFE with controls. Two-invoice system in China. 13 cohorts, all eventually treated.
& 0
& ``Baseline: Two-way fixed effects model for the impact of TIS on drug prices'' (Table~3) \\

\textcite{estrada2024dismissal}
& Left school after 1 year (Table 2, col.~1)
& Rule i --- Chilean reform of 2014. Simple DiD (treated $\times$ post).
& 0
& ``Our main outcomes are dummy variables for whether the teacher was not working in the same public school'' (p.~12) \\

\textcite{sarmiento2023air}
& PM10 (particulate matter)
& Rule i --- CS-DD is the article's primary estimator. TWFE on annual data for comparability.
& 0
& ``We select the doughnut design as our preferred specification'' (p.~9) \\

\textcite{kresch2020buck}
& Total investment / 1000 (Table 3, col.~1)
& Rule i --- Total investment of Brazilian municipalities. Single cohort: all treated in 2006 (Fiscal Responsibility Law).
& 0
& ``the main specification'' (fn.~11) \\

\textcite{myers2017power}
& Prob.\ first birth before age 19
& Rule i --- TWFE uses continuous treatment (fraction of ages 14--17 with pill access). CS/SA/Gardner use discretized binary version.
& 0
& ``Using the results from model 3'' (p.~2200) \\

\textcite{soliman2025disrupting}
& MME per capita $\times$ 10 (Table 1, col.~1)
& Rule i --- DEA crackdown on pain clinics. Staggered county-year panel.
& 0
& ``State-by-year fixed effects \ldots\ are included in my preferred specification'' (p.~175) \\

\textcite{moorthy2025bluecollar}
& Log earnings, generation 1 (Figure 2)
& Rule ii --- Largest $N$. Mortality data (Table 6) requires restricted access not available in the package.
& 0
& ``Our baseline specification uses the IHS of mortality as the outcome variable and controls for the relevant contemporaneous population'' (p.~12) \\

\textcite{bancalari2024unintended}
& Infant mortality rate (Table 2, PA, col.~1)
& Rule i --- Baseline specification without controls. TWFE $= +0.74$ (SE $= 0.42$).
& 0
& ``The main finding of this paper underscores an increase in early-life mortality during the implementation of sewerage infrastructure'' (p.~16) \\

\textcite{gandhi2025alleviating}
& Nursing hours ratio (binarized treatment)
& Rule i --- Article uses continuous treatment (Illinois $\times$ post). Treatment binarized for CS-DID.
& 0
& ``Figure 1 previews our main result'' (p.~9) \\

\textcite{anderson2024imposing}
& Black post-neonatal mortality
& Rule i --- Hospital desegregation via Medicare. Staggered treatment 1967--1973 (7 cohorts).
& 0
& ``the fully specified regression model'' (p.~16) \\

\textcite{axbard2024informed}
& Any environmental enforcement action (Table 1a, col.~1)
& Rule i --- Treatment = firm within 10km of monitor $\times$ post-2015. Binary outcome (0/1). Single treatment date.
& 0
& ``we include the distances \ldots\ in our main specification and interact the distance bins with the time fixed effects'' (p.~233) \\

\textcite{bhalotra2023maternal}
& Log maternal mortality ratio (col.~4)
& Rule i --- Reserved legislative quotas for women. 22 countries, staggered adoption 1989--2013. No controls at baseline.
& 0
& ``we use this estimator as our main specification'' (p.~2181) \\

\textcite{sekhri2024curse}
& High-yield variety adoption (Table 3, col.~2)
& Rule ii --- Largest $N$. Health outcomes (Table 9) require restricted NFHS data not available in the package.
& 0
& ``our preferred specification includes district fixed effects, state $\times$ birth-year fixed effects, and district-specific linear trends'' (p.~4) \\

\textcite{steffens2025smoking}
& Smoking prevalence (Figure 3a)
& Rule i --- Main result from Figure 3a. Single-timing DiD (2009 cohort).
& 0
& ``The main specification in this paper is based on a generalized difference-in-differences design'' (p.~7) \\

\textcite{arbogast2024burdens}
& Medicaid/CHIP enrollment rate
& Rule i --- Administrative burdens and enrollment. 15 treated states, 12 staggered cohorts. Dataset reconstructed via Census API.
& 0
& ``premium changes, income cutoffs, and work requirements are controlled for in the baseline specifications'' (p.~12) \\

\textcite{arthi2022recessions}
& Total census mortality rate (Table 2, col.~1)
& Rule i --- Baseline specification. Classic 2$\times$2 DiD: 538 districts, 2 periods (1851, 1861). No controls.
& 0
& ``our preferred all-age results in column~3 of Table~2 imply that the cotton shock generated 24,418 excess deaths'' (p.~247) \\

\textcite{brodeur2025shootings}
& Log employment/population (Table 2, col.~1)
& Rule iii(c) --- Documented random selection. Mass shootings and local employment.
& 0
& ``Our preferred specification includes Census divisions $\times$ year fixed effects'' (p.~116) \\

\textcite{johnson2024legal}
& Log accident rate (Table 2, col.~1)
& Rule i --- TWFE with state+year FEs. Simplest specification. Retaliatory discharge protection and workplace safety.
& 0
& ``Our main specification is as follows'' (p.~1242) \\

\textcite{galasso2024licensing}
& Drug access (binary)
& Rule i --- Medicines Patent Pool. 7 treatment cohorts (2011--2017). 84.6\% never treated.
& 0
& ``Table 2 provides the baseline results'' (Section VI.A) \\

\textcite{xu2023bureaucratic}
& Log deaths at city level (Table 2, col.~3)
& Rule i --- 1918 pandemic and bureaucratic representation in India. Single treatment timing.
& 0
& ``Since the main results also hold for this subsample \ldots\ the results will still be informative'' (p.~490) \\

\textcite{prem2023rise}
& Coca area per grid cell
& Rule i --- Article uses continuous treatment (suitability $\times$ announcement); binarized at median for CS-DID. Single date 2014.
& 0
& ``Our preferred specification controls for a large set of predetermined municipal characteristics'' (p.~347) \\

\textcite{clarke2021abortion}
& Abortion-related morbidity / 1000 pop (Table 2, PA, col.~1)
& Rule i --- Legalization in Mexico City's Federal District (March 2007). Single treated unit.
& 0
& ``Our preferred estimates are those including population weights with full time-varying controls'' (p.~13) \\

\textcite{lemoglie2022mafia}
& Log new enterprises (Table 2, col.~5)
& Rule i --- Mafia $\times$ 2007 financial crisis. Full model with controls + North $\times$ year interactions.
& 0
& ``we refer to the most complete specification in column 5 as the `complete model'\,'' (p.~150) \\

\textcite{cameron2021crimes}
& Positive biological STI test (Table II, col.~1, PA)
& Rule i --- Criminalization of sex work in Malang, Indonesia. Single treatment (November 2014), 2 periods.
& 0
& ``The main specification used in the analysis is'' (p.~440) \\

\textcite{courtemanche2025calorie}
& BMI (Table 3, col.~1)
& Rule i --- Calorie labeling laws. County FE + monthly FE + county linear trends.
& 0
& ``main two-way fixed-effects estimates'' (footnote~29, p.~1692) \\

\textcite{bargain2019women}
& Composite empowerment index (Table 1, col.~4)
& Rule i --- Arab Spring in Egypt. Model 4 (baseline). 2 periods (2008, 2014).
& 0
& ``we estimate our main difference-in-difference model as follows'' (Section 3.3) \\

\textcite{anderson2019tuberculosis}
& Log pulmonary TB mortality (Table 3B, col.~1)
& Rule i --- Anti-TB public health campaign (1900--1917). 548 cities, 16 staggered cohorts.
& 0
& ``baseline regression'' (p.~151); Section IV: ``Baseline Results'' \\

\textcite{kuziemko2018managed}
& Black infant mortality $\times$100 (Table 3)
& Rule i --- Managed care in Texas. 71 treated counties (7 cohorts: 1993--2006), 179 never treated.
& 0
& ``Our preferred specification includes county linear time trends'' (p.~261) \\

\textcite{malkova2018maternity}
& General fertility rate (official)
& Rule ii --- Soviet maternity benefits. All eventually treated: 2 cohorts (1981, 1982). 82 oblasts. Equation (1) is the foundational specification; Table 2 presents initial results.
& 0
& --- \\

\textcite{rossinslater2017signing}
& Married to biological father (Table 3, col.~5)
& Rule i --- Paternity establishment. 44 states, 8 staggered cohorts (1990--1999). Primary aggregate indicator.
& 0
& ``the main results presented in the above tables'' (Tables 8--9) \\

\textcite{kahn2015water}
& Chemical Oxygen Demand, mg/L (Table 3, col.~2)
& Rule ii+iii(a) --- 2006 policy change in China. Single timing. 497 stations, 7 years. Table 3 (station FE) is the most demanding specification; col.~2 (COD) is the most aggregated pollutant.
& 0
& --- \\

\textcite{bailey2015war}
& Age-adjusted mortality, elderly (Table 2, PB, col.~2)
& Rule i --- Article title emphasizes ``Mortality of Older Americans''. Figure 7D is the main event study. Staggered CHC rollout 1965--1974.
& 0
& ``our baseline specification of equation (1)'' (Figures 5, 8, 9) \\

\textcite{gallagher2014learning}
& Log(flood insurance policies per capita + 1) (Figure 2)
& Rule i --- Equation (1) described as ``the main estimating equation''. Only event study coefficients reported.
& 1
& ``Equation~(1) is the main estimating equation'' (p.~214) \\

\textcite{deangelo2014life}
& Fatalities / VMT (Table 4, col.~1)
& Rule ii+iii(a) --- Largest $N$: full US sample ($N$=3384) vs.\ geographic control WA+ID ($N$=216). iii(a): fat\_vmt (aggregate) over fat\_good\_vmt (subcategory).
& 0
& --- \\

\textcite{hausman2014corporate}
& Collective dose per person-rem (Table 6, col.~1)
& Rule i+iii(a) --- Production outcomes use Poisson/NB (incompatible with template). personrem chosen as aggregate measure (collective dose) over rem (worker average). Nuclear divestiture, 9 cohorts.
& 0
& ``the preferred specification is an unconditional negative binomial'' (p.~192) \\

\textcite{danzer2023pensions}
& Fertility (Table 3, col.~2)
& Rule i --- Pension reform in Brazil (1991). DiD = TREAT $\times$ AFTER. RCS (PNAD). Single timing.
& 0
& ``None of the alternative specifications alter our main results'' (p.~160) \\

\textcite{jayachandran2010modern}
& Log mortality rate (Table 4, PB, col.~1)
& Rule i --- Disease-time DiD: MMR (treated) vs.\ TB (control) before/after sulfonamides (1937). State panel 1925--1943.
& 0
& ``the slope-change model is our preferred specification'' (p.~131) \\

\textcite{fisman2017distortionary}
& I(Deaths/Quota $>$ 1) (Table 2, col.~1)
& Rule ii --- LPM binary outcome. Staggered NSNP law adoption by 19 provinces (2005--2012). China's death quota program. Col.~1 = full sample.
& 0
& --- \\

\textcite{cao2023mitigating}
& Fire count within 0--90km (Table 2, col.~3)
& Rule i --- Biomass power plants and agricultural fires. Staggered treatment. 954 plants, monthly data 2001--2019.
& 0
& ``In the main results, we use land type classifications to identify hotspots in cropland'' (p.~10) \\

\end{longtable}
\end{small}

\medskip\noindent
\textit{Notes:} Collapse = 0 indicates that the static ATT is directly available in the article; Collapse = 1 indicates that only event study coefficients were reported and the static ATT was re-estimated with a single post-treatment indicator. The selection rules follow: (i) author-declared preference; (ii) largest sample size; (iii-a) broadest conceptual scope; (iii-b) greatest parsimony; (iii-c) documented random selection. When the textual quote is not available (``---''), the decision was based on reading the article and replication package, documented in the corresponding \texttt{metadata.json} file. Complete article cards are in Appendix~\ref{AppendixB}.
